M.Sc. Proposal: \\ \bigskip Computational Electrokinetics

### 2013-02-09 notes/thesis-latex-template/thesis.tex
Update thesis.

When $\beta$ becomes large, the salt concentration $C$ near the front of the particle 
(at $\theta \approx 0$) approaches zero, while creating a wake behind the particle 
(at $\theta \approx \pi$).
This is results in high gradients in $\log C$ near the front of the particle (Figures \ref{fig:LargeBeta_C1}, \ref{fig:LargeBeta_C2} and
\ref{fig:LargeBeta_C3}) and, therefore, strong electric field $\bE$ form near the particle surface (Figures \ref{fig:LargeBeta_Phi1}, \ref{fig:LargeBeta_Phi2} and \ref{fig:LargeBeta_Phi3}) due to effective boundary conditions at Eq. \ref{eq:ephor_bnd}. 
The streamline pattern doesn't change drastically for different electric field magnitudes, as shown in Figure \ref{fig:LargeBeta_Psi1}, \ref{fig:LargeBeta_Psi2} and \ref{fig:LargeBeta_Psi3}. 
The resulting flow pattern is similar to the Stokes creeping flow, as shown in Figure
\ref{fig:LargeBeta_PsiStokes}.

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
        \caption[$\beta = 0.1$ results for $\Psi$]
        {$\beta = 0.1$ streamlines results: grid size $512 \times 512$, 
        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
        The numerical results for $\Psi$ is scaled by $\beta^{-1}$, so the linear regime
        will appear the same for different $\beta$ values.}
	    \label{fig:LargeBeta_Psi1}	    
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
        \caption[$\beta = 0.8$ results for $\Psi$]
        {$\beta = 0.8$ streamlines results: grid size $512 \times 512$, 
        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
        The numerical results for $\Psi$ is scaled by $\beta^{-1}$, so the linear regime
        will appear the same for different $\beta$ values.}
	    \label{fig:LargeBeta_Psi2}	    
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
        \caption[$\beta = 5.0$ results for $\Psi$]
        {$\beta = 5.0$ streamlines results: grid size $512 \times 512$, 
        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
        The numerical results for $\Psi$ is scaled by $\beta^{-1}$, so the linear regime
        will appear the same for different $\beta$ values.}
	    \label{fig:LargeBeta_Psi3}	    
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=1\textwidth]{figs/LinearStokes_Psi.eps}
        \caption[Stokes flow results]
        {Stokes flow streamlines results: grid size $512 \times 512$, 
        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
        The numerical results for $\Psi$ is scaled by $\beta^{-1}$, so the linear regime
        will appear the same for different $\beta$ values. Note that the numerical results
        show very similar flow pattern to the analytical Stokes flow.}
	    \label{fig:LargeBeta_PsiStokes}	    
    \end{center}
\end{figure}

>>>>

When $\beta$ becomes large, the salt concentration $C$ near the front of the particle 
(at $\theta \approx 0$) approaches zero, while creating a wake behind the particle 
(at $\theta \approx \pi$).
This is results in high gradients in $\log C$ near the front of the particle (Figures \ref{fig:LargeBeta_C1}, \ref{fig:LargeBeta_C2} and
\ref{fig:LargeBeta_C3}) and, therefore, strong electric field $\bE$ form near the particle surface (Figures \ref{fig:LargeBeta_Phi1}, \ref{fig:LargeBeta_Phi2} and \ref{fig:LargeBeta_Phi3}) due to effective boundary conditions at Eq. \ref{eq:ephor_bnd}. 
The streamline pattern doesn't change drastically for different electric field magnitudes. 
The resulting flow pattern is similar to the Stokes creeping flow, as shown in Figure
\ref{fig:LargeBeta_Psi}.

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=.45\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
    \includegraphics[width=.45\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
    \includegraphics[width=.45\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
    \includegraphics[width=.45\textwidth]{figs/LinearStokes_Psi.eps}
        \caption[Streamfunction results]
        {$\beta = 0.1, 0.8, 5.0$ and Stokes streamlines results: grid size $512 \times 512$, 
        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
        The numerical results for $\Psi$ is scaled by $\beta^{-1}$, so the linear regime
        will appear the same for different $\beta$ values.
        Note that the numerical results show very similar flow pattern to the analytical Stokes flow.}
	    \label{fig:LargeBeta_Psi}	    
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=.45\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[-1]_Psi.eps}
    \includegraphics[width=.45\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[-1]_Psi.eps}
    \includegraphics[width=.45\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[-1]_Psi.eps}
    \includegraphics[width=.45\textwidth]{figs/LinearStokes_Psi.eps}
        \caption[Streamfunction ''reversed''  results]
        {$\beta = 0.1, 0.8, 5.0$ and Stokes streamlines ''reversed'' results: grid size $512 \times 512$, 
        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
        The numerical results for $\Psi$ is scaled by $\beta^{-1}$, so the linear regime
        will appear the same for different $\beta$ values.
        Note that the numerical results show very similar flow pattern to the analytical Stokes flow.}
	    \label{fig:LargeBeta_Psi}	    
    \end{center}
\end{figure}
